Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-31 ProbabilisticCoherence.tex
Cleaned up definitions of coherence, moved figure, comment out discussion about densities

We will also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$

\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
  Suppose $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ denotes point forecasts of each series in the hierarchy at time $t+h$.  Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathbb{C}$. 
\end{definition}

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple, where $\mathscr{F}^m$ is a $\sigma$-algebra on $\mathbb{R}^m$. Then, $(\mathbb{C}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be a coherent probability measure space iff
  $$
      \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F}^m,
    $$ 
  where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$. 
\end{definition}

We illustrate Definition~\ref{def:cohprob} in Figure~\ref{fig2}, showing $\bm{S}$ mapping any set $\bm{A}\in\mathbb{R}^m$ to the coherent space.

@@

    \node at (0,5) {$\mathbb{R}^m$(domain of $\bm{S}$)};
    \node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
    \node at (4,1.0) {$\mathbb{C}^m$};
    %\node[bullet,label=below:$f(x)$] at (4,2.5){};

@@

    \end{tikzpicture}
    \newline
  \end{center}
  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to $\mathbb{C}^m$ through the mapping $\bm{S}$.}\label{fig2}
\end{figure}

Definition~\ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$. That is, a \textit{coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.

The following example will help to understand these definitions more clearly.

Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top level series $Tot$. Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$. Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$. This implies that, even though  $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$, the points actually lie in $\mathbb{C}^2$, which is a two dimensional subspace within that $\mathbb{R}^3$ space. Therefore, any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$ is impossible, so that $f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$.

>>>>

We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$. We also note that when $\bm{S}$ is understood as a linear mapping $\bm{S}:\mathbb{R}^m\rightarrow\mathbb{R}^n$ whose image given by the coherent space $\mathfrak{s}$. This is depicted in Figure~\ref{fig2}.

@@

    \node at (0,5) {$\mathbb{R}^m$(domain of $\bm{S}$)};
    \node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
    \node at (4,1.0) {$\mathfrak{s}$};
    %\node[bullet,label=below:$f(x)$] at (4,2.5){};

@@

    \end{tikzpicture}
    \newline
  \end{center}
  \caption{The domain, codomain and image of the mapping $\bm{S}$.}\label{fig2}
\end{figure}

\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
  Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$,  made using information up to and including time $t$.  Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$. 
\end{definition}

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  Let $(\mathbb{R}^m, \bm{\mathscr{F}}, \nu)$ be a probability triple, where $\mathscr{F}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$. Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.  Here $\mathscr{F}_{\mathfrak{s}}$ is formed as collection of sets $\bm{S}(\bm{A})$, where $\bm{S}(\bm{A})$ denotes the image of the set $\bm{A}\in \mathscr{F}$ under the mapping $\bm{S}$.  Then $\breve{\nu}$ is said to be a \emph{coherent probability measure} iff
  $$
      \breve{\nu}(\bm{S}(\bm{A})) = \nu(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F},
    $$  
\end{definition}

%Definition~\ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$. That is, a \textit{coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.

%The following example will help to understand these definitions more clearly.

%Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top level series $Tot$. Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$. Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$. This implies that, even though  $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$, the points actually lie in $\mathbb{C}^2$, which is a two dimensional subspace within that $\mathbb{R}^3$ space. Therefore, any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$ is impossible, so that $f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$.
